A weakly structured stem for human origins in Africa

### 2022-01-17 paper.tex

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig4}
    \caption{
        \textbf{Model validation using independent statistics.} (A--C) Using
        our best fit models to the LD and pairwise diversity statistics, we
        simulated expected conditional site-frequency-spectra (cSFS) and
        compared to the observed cSFS from the data. Our inferred models
        provide a good fit to the data, even though these were not used in our
        inference. Across the three populations, ancestral state
        misidentification was consistently inferred to be 1.5--1.7\% for
        intergenic loci (Supp. Methods). (D, E) We used Relate
        \citep{Speidel2019-nj} to reconstruct genome-wide gene genealogies,
        which we used to estimate coalescence rate trajectories. While
        coalescence rate distributions are informative statistics about past
        evolutionary processes, interpretation can be hindered by migration and
        population structure. Translating relative cross-coalescence curves
        into population divergences is especially prone to misinterpretation.
    }
    \label{fig:4}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig4}
    \caption{
        \textbf{Model validation using independent statistics.} (A--C) Using
        our best fit models to the LD and pairwise diversity statistics, we
        simulated expected conditional site-frequency-spectra (cSFS) and
        compared to the observed cSFS from the data. Our inferred models
        provide a good fit to the data, even though these were not used in our
        inference. Across the three populations, ancestral state
        misidentification was consistently inferred to be 1.5--1.7\% for
        intergenic loci (Supp. Methods). (D, E) We used Relate
        \citep{Speidel2019-nj} to reconstruct genome-wide gene genealogies,
        which we used to estimate coalescence rate trajectories and
        and cross-coalescence rates between pairs of populations. While
        coalescence rate distributions are informative statistics about past
        evolutionary processes, interpretation can be hindered by migration and
        population structure, and translating relative cross-coalescence rate
        curves (RCCR) into population divergence times is especially prone
        to misinterpretation. For example, the Mende-Gumuz comparison shows
        a more recent increased RCCR than either population with the British,
        a pattern that is recapitulated under our best-fit model, even though
        the Mende-Gumuz split occurs prior to the Gumuz-British split.
    }
    \label{fig:4}
\end{figure}
